Supplemental material for `Eliminating object prior-bias from sparse-projection tomographic reconstructions'

### 2021-10-15 paper/changes.tex
Tuning of parameters is now placed in results section; comparision with literature is removed in supplementary material, cross-ref included while introducing lambda 1 and 2

    That said, the goal of our previous and curent work is to provide
    a technique that can improve upon a chosen baseline reconstruction
    when measurements are extremely sparse.  One may choose any
    baseline reconstruction (including an inferior -- for this dataset
    -- Compressed sensing prior) for pedagogical, historical, or
    commercial reasons, and given that, our key question is -- is
    there a way to improve?  The spatially-varying method of
    moderating the prior settles this question.

>>>>

    \textit{That said, the goal of our previous and curent work is to provide
    a technique that can improve upon a chosen baseline reconstruction
    when measurements are extremely sparse.  One may choose any
    baseline reconstruction (including an inferior -- for this dataset
    -- Compressed sensing prior) for pedagogical, historical, or
    commercial reasons, and given that, our key question is -- is
    there a way to improve?  The spatially-varying method of
    moderating the prior settles this question.}

### 2021-10-15 paper/post_tci.tex
Tuning of parameters is now placed in results section; comparision with literature is removed in supplementary material, cross-ref included while introducing lambda 1 and 2

There also exist methods for estimating new changes (in the test)
directly in projection space. In such techniques which can be used in
longitudinal studies, the object-prior is projected in the same set of
views as the current set of test measurements, and a set of projection
differences is computed. These projection differences are essentially
tomographic projections of differences between the unknown test and
the known object-prior. Hence, a variety of reconstruction algorithms
can be used to estimate such a difference image which can then be
added to the object-prior to yield the final estimate of the
test. Such methods have been proposed
in~\cite{Pourmorteza2015,Lee2012}. However, reconstruction of the
difference image will inherently contain sub-sampling artefacts, and
these artefacts will appear in the final reconstruction as there is no
mechanism to mitigate them (unlike the method that we propose). This
can be seen in Sec.~4 of our supplementary material~\cite{supp_paper},
where we have compared our method with~\cite{Lee2012}.

@@

$\lambda_1$ and  $\lambda_2$ are tunable weights given to the
TV-prior and object-prior terms respectively. The unknowns
$\boldsymbol{x}$ and $\boldsymbol{\alpha}$ are solved by alternately
minimizing $J_{\boldsymbol{\alpha}}(\boldsymbol{x})$ using a fixed
$\boldsymbol{\alpha}$, and $J_{\boldsymbol{x}}(\boldsymbol{\alpha})$
using the resultant $\boldsymbol{x}$.
$J_{\boldsymbol{\alpha}}(\boldsymbol{x})$ is solved for using an
optimal first-order method for large-scale TV regularization presented
in~\cite{TVReg} and available in~\cite{TVReg-lib}.

@@

% \begin{equation}
%   \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
%     \hat{\boldsymbol{x}}(i))^2}.
%  \end{equation}
RMSE corresponds to error in intensity values and is a measure of
absolute error. For purposes of normalization, while reporting numbers
we rescale intensity values of both the ground truth and the
reconstructed results to lie between 0 to 1, so that the best possible
RMSE is 0, and the worst value is 1.  On the other hand, SSIM seeks
to consider perceptual changes, as well as correlation between
adjacent pixels. This can be useful in a clinical context.  Here, we
therefore assign a higher weightage to structure preservation, that is
we assign the following weights to structure, contrast, and intensity
respectively: $0.7,0.2,0.1$.

Our results are optimized for SSIM, but it can be verified that in all
cases for the various datasets considered, our results are favourable
with either metric.
%The reason for emphasizing the structure with an
%exponent of 0.7 stems from the optimization process since the
%intensity span (and, in general, the histogram) of reconstructed volumes
%differ across various methods and solvers.

@@

\subsection{Reconstruction of datasets with imaging model available}
\subsubsection{\textbf{Potato}}
\label{Sec:potato_spatially_varying}

@@

\subsection{Reconstruction of datasets without imaging model}
\subsubsection{\textbf{Liver}}
\label{sec:tmh}

@@

\section{Discussion}
\label{sec:discussion}
In this section, we discuss tuning of parameters, computational
complexity of our method, and requirements for applying deep learning
techniques in longitudinal few-view reconstruction.

\subsection{Tuning of parameters}
$\lambda_1$, $\lambda_2$ and $k$ are the three hyper-parameters that
need to be chosen carefully for optimal reconstruction. In our
experiments, $\lambda_1$ was tuned in such a way as to maximize the
SSIM of the complete reconstructed test volume using the TV-only
regularizer.  In particular, the RoI was not considered.  Now, this
value was retained for our spatially-varying prior-based
reconstruction as well.  In principle, one could have jointly
optimized both $\lambda_1$ and $\lambda_2$ to get even better results
compared to the one we have in Section~\ref{results}.  The value of
$\lambda_2$ largely depends on the amount of artefacts one aims to
remove by using object-prior at the cost of their dominance in the new
regions. This value was chosen to lie between $0-3$ for our datasets
(having the fixed $\lambda_1$).
\subsection{Computational Complexity}

>>>>

There also exist methods for estimating new changes (in the test)
directly in projection space. In such techniques which can be used in
longitudinal studies, the object-prior is projected in the same set of
views as the current set of test measurements, and a set of projection
differences is computed. These projection differences are essentially
tomographic projections of differences between the unknown test and
the known object-prior. Hence, a variety of reconstruction algorithms
can be used to estimate such a difference image which can then be
added to the object-prior to yield the final estimate of the
test. Such methods have been proposed
in~\cite{Pourmorteza2015,Lee2012}. However, reconstruction of the
difference image will inherently contain sub-sampling artefacts, and
these artefacts will appear in the final reconstruction as there is no
mechanism to mitigate them (unlike the method that we propose). %This
%can be seen in Sec.~4 of our supplementary material~\cite{supp_paper},
%where we have compared our method with~\cite{Lee2012}.

@@

$\lambda_1$ and  $\lambda_2$ are tunable weights given to the
TV-prior and object-prior terms respectively. Their selection is discussed in
Section.~\ref{sec:tuning_parameters}. The unknowns
$\boldsymbol{x}$ and $\boldsymbol{\alpha}$ are solved by alternately
minimizing $J_{\boldsymbol{\alpha}}(\boldsymbol{x})$ using a fixed
$\boldsymbol{\alpha}$, and $J_{\boldsymbol{x}}(\boldsymbol{\alpha})$
using the resultant $\boldsymbol{x}$.
$J_{\boldsymbol{\alpha}}(\boldsymbol{x})$ is solved for using an
optimal first-order method for large-scale TV regularization presented
in~\cite{TVReg} and available in~\cite{TVReg-lib}.

@@

% \begin{equation}
%   \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
%     \hat{\boldsymbol{x}}(i))^2}.
%  \end{equation}
RMSE corresponds to error in intensity values and is a measure of
absolute error. For purposes of normalization, while reporting numbers
we rescale intensity values of both the ground truth and the
reconstructed results to lie between 0 to 1, so that the best possible
RMSE is 0, and the worst value is 1.  On the other hand, SSIM seeks to
consider perceptual changes, as well as correlation between adjacent
pixels. This can be useful in a clinical context.  Here, we therefore
assign a higher weightage to structure preservation, that is we assign
the following weights to structure, contrast, and intensity
respectively: $0.7,0.2,0.1$. Our results are optimized for SSIM, but
it can be verified that in all cases for the various datasets
considered, our results are favourable with either metric.

Here below, we first discuss tuning of parameters followed by the
rationale for using multiple eigenspaces to compute weightsmap. We
then present reconstruction results for each of the datasets.
%The reason for emphasizing the structure with an
%exponent of 0.7 stems from the optimization process since the
%intensity span (and, in general, the histogram) of reconstructed volumes
%differ across various methods and solvers.

\subsection{Tuning of parameters}
\label{sec:tuning_parameters}
$\lambda_1$, $\lambda_2$ and $k$ are the three hyper-parameters that
need to be chosen carefully for optimal reconstruction. In our
experiments, $\lambda_1$ was tuned in such a way as to maximize the
SSIM of the complete reconstructed test volume using the TV-only
regularizer.  In particular, the RoI was not considered.  Now, this
value was retained for our spatially-varying prior-based
reconstruction as well.  In principle, one could have jointly
optimized both $\lambda_1$ and $\lambda_2$ to get even better results
compared to the one we have in Sections~\ref{sec:results_with_imaging_model}, and~\ref{sec:results_without_imaging_model}.  The value of
$\lambda_2$ largely depends on the amount of artefacts one aims to
remove by using object-prior at the cost of their dominance in the new
regions. This value was chosen to lie between $0-3$ for our datasets
(having the fixed $\lambda_1$).

@@

\subsection{Reconstruction of datasets with imaging model available}
\label{sec:results_with_imaging_model}
\subsubsection{\textbf{Potato}}
\label{Sec:potato_spatially_varying}

@@

\subsection{Reconstruction of datasets without imaging model}
\label{sec:results_without_imaging_model}
\subsubsection{\textbf{Liver}}
\label{sec:tmh}

@@

\section{Discussion}
\label{sec:discussion}
In this section, we discuss computational
complexity of our method and requirements for applying deep learning
techniques in longitudinal few-view reconstruction.
\subsection{Computational Complexity}

### 2021-10-15 paper/post_tci_supplementary.tex
Tuning of parameters is now placed in results section; comparision with literature is removed in supplementary material, cross-ref included while introducing lambda 1 and 2

\item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, use
  these in the alternate minimization optimization described in Eq.~7
  of the main paper.
\end{enumerate}

We mention in passing that if we are to entirely avoid the other
parameters (viz. $\lambda_1$ and $\lambda_2$, the prior and the pilot
can be stitched in a simplistic way using the equation 
$\boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
The advantage of this method is that the computational time is
signficantly reduced since the alternate minimization procedure is not
used.

@@

@@

\begin{table}[!h]
  \centering
      \caption{SSIM values (within RoI) of reconstructions shown in Figure~\ref{fig:comparisonLit_results}.}
  \begin{tabular}{|l|l|l|}
\hline
 & \textbf{SSIM (whole image)} & \textbf{SSIM (RoI)} \\ \hline
\textbf{Method in~\cite{Lee2012}} & 0.65 & 0.60 \\ \hline
\textbf{\begin{tabular}[c]{@{}l@{}}This paper\end{tabular}} & 0.89 & 0.92 \\ \hline
  \end{tabular}
  \label{tab:comparisonLit}
\end{table}
%\clearpage
%\newpage

\bibliography{tci_ref}
\end{document}

>>>>

\item Once the binary weights-map $\boldsymbol{W_b}$ is obtained, use
  these in the alternate minimization optimization described in Eq.~3
  of the main paper.
\end{enumerate}

We mention in passing that if we are to entirely avoid the other
parameters (viz. $\lambda_1$ and $\lambda_2$), the prior and the pilot
can be stitched in a simplistic way using the equation 
$\boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
The advantage of this method is that the computational time is
signficantly reduced since the alternate minimization procedure is not
used.

@@

\end{document}

@@

\begin{table}[!h]
  \centering
      \caption{SSIM values (within RoI) of reconstructions shown in Figure~\ref{fig:comparisonLit_results}.}
  \begin{tabular}{|l|l|l|}
\hline
 & \textbf{SSIM (whole image)} & \textbf{SSIM (RoI)} \\ \hline
\textbf{Method in~\cite{Lee2012}} & 0.65 & 0.60 \\ \hline
\textbf{\begin{tabular}[c]{@{}l@{}}This paper\end{tabular}} & 0.89 & 0.92 \\ \hline
  \end{tabular}
  \label{tab:comparisonLit}
\end{table}
%\clearpage
%\newpage
\bibliography{tci_ref}
